Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with stable Branching

### 2019-02-11 supCLT.tex
supCLT.tex: 0211
supCLT.tex: deleted %


supCLT.tex: 0131


working

%%----Versions-----------------------------
% supCLT0128.tex 2018/01/28 by Renming
% supCLT0127.tex 2018/01/27 by Yanxia
% supCLT0124.tex 2018/01/24 by Jianjie
% supCLT0114.tex 2018/01/14 by Yanxia
% supCLT0107.tex 2018/01/07 by Jianjie
% supclt1231.tex 2018/12/14 by Zhenyao
% supclt1213.tex 2018/12/14 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
	\setlength{\textwidth}{\paperwidth}
	\addtolength{\textwidth}{-2in}
	\calclayout
\usepackage[utf8]{inputenc}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
\usepackage{cite}
\usepackage[backref=section]{hyperref}
	\def\MR#1{\href{http://www.ams.org/mathscinet-getitem?mr=#1}{MR-#1}}
	\def\ARXIV#1{\href{https://arxiv.org/abs/#1}{arXiv:#1}}
\usepackage{comment}
\usepackage{amsthm}
	\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
	\newtheorem{conj}[thm]{Conjecture}
	\theoremstyle{definition}
	\newtheorem{defi}[thm]{Definition}
	\newtheorem{rem}[thm]{Remark}
	\newtheorem{exa}[thm]{Example}
	\newtheorem{asp}{Assumption}
	\numberwithin{equation}{section}
	\allowdisplaybreaks
%\newcommand{\added}[1]{{\color{blue}#1}}\newcommand{\deleted}[1]{{\color{red}#1}}
%\newcommand{\added}[1]{#1}\newcommand{\deleted}[1]{}

%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
 %   {CLT for Super-OU Processes with stable Branching}
% {Central Limit Theorems for Super Ornstein-Uhlenbeck Processes with Stable Branching}
{Stable Central Limit Theorems for Super OU Processes with Stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren\\
    LMAM School of Mathematical Sciences \& Center for
Statistical Science\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
%new
\address
{Renming Sond\\
Department of Mathematics\\
University of Illinois of Illinois at Urbana-Champaign\\
Urbana, IL 61801, USA}
\email{rsong@illinois.edu}
\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
%end new
\address
    {Zhenyao Sun\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao\\
    School of Mathematical Sciences\\
    Peking University\\
    Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
\begin{abstract}
 Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z)$, 
 where $\alpha >0$ and $\beta\in (0,1)$ and 
% that there exists $C >0$ and $\delta >0$ such that
$psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
$
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).
$
    For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
    In the small branching rate case  $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$,  $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
 In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$,
we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$,
and then established a central limit theorem, 
%which say that after proper centering and scaling, we get a $(1+\beta)$-stable random variable again.
which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges
weakly to a $(1+\beta)$-stable random variable.
\end{abstract}
%\begin{abstract}
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------

%\maketitle
%\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}

\section{Introduction}
\subsection{Model}
\label{ss:1.1}
	Let $d \in \mathbb N:= \{1,2,\dots\}$.
    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck prcess (OU process) with generator
\begin{equation}
\label{eq: OU generator}
    Lf(x)
        = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
        \quad  x\in \mathbb R^d,
        f \in C^2(\mathbb R^d),
\end{equation}
    where $\sigma$ and $b$ are positive constants.
    Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
    Let $\psi$ be the function on $\mathbb R_+$ defined by
\begin{equation}
\label{mechanism}
       \psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
%    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
%    Denote by $\mathcal B(\mathbb R^d)$ the space of all real-valued Borel measurable functions on $\mathbb R^d$.
We use $B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
	For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
 We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.

    We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{equation} \label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation}\label{eq1}
	V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}	
    The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.

   According to  Subsection A.1, the branching mechanism $\psi$ can be extended to
    $\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 \[\psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb C_+,\]
    which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    \{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
\begin{equation}
\label{eq: deriavetive of the Poission part}
    \psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    \quad z\in \mathbb C^0_+.
\end{equation}
{ \bf
\begin{asp}
\label{asp: branching mechanism}
    The branching mechanism takes the form of
\[
    \psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
\]
%    where $\eta > 0$, $\gamma \in (0,1)$ and 
   where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and 
    %that there exists $C >0$ and $\delta >0$ such that
    and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
\[
    |\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
\]
\end{asp}
\begin{lem}
    Under Assumption \ref{asp: branching mechanism}, we have that $\psi$ satisfies the Grey's condition i.e. there is some constant $z' > 0$ such that $\psi(z) > 0$ for all $z>z'$, and that $\int_{z'}^\infty \psi(z)^{-1}dz < \infty$.
    Also, $\psi$ satisfies the $L \log L$ criterion  i.e.,
\[
    \int_1^\infty y \log y~\pi(dr)< \infty.
\]
\end{lem}
\begin{proof}
    { Need a proof.}
\end{proof}
}
    According to \cite[Theorems 12.5 \& 12.7]{Kyprianou2014Fluctuations}, we have
\begin{equation}
    \mathbb{P}_{\mu} (\exists t\geq 0,~\text{s.t.}~\|X_t\|=0)
    = e^{-\bar v \|\mu\|},
\end{equation}
    where $\bar v := \sup\{\lambda \geq 0: \psi(\lambda) = 0\}$.
    Define
\begin{equation}\label{meansemigroup}
    P^{\alpha}_t f(x)
    :=
    e^{\alpha t} P_t f(x) =
    \Pi_x [e^{\alpha t}f(\xi_t)],
    \quad x\in \mathbb R^d,t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+).
\end{equation}
    It is konwn that, see \cite[Proposition 2.27]{Li2011Measure-valued} for example, $(P^\alpha_t)_{t\geq 0}$ is the \emph{mean semigroup} of $X$, in the sense that
\begin{equation}\label{eq:meanformula}
    \mathbb{P}_{\mu}[\langle f, X_t \rangle]
    = \langle P^\alpha_t f, \mu \rangle,
    \quad t\geq 0, f\in \mathcal B(\mathbb R^d, \mathbb R_+), \mu \in \mathcal M(\mathbb R^d).
\end{equation}

 In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
 $$\frac{\langle f, X_t \rangle -G_t}{F_t}$$ converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral 
 %decomposition.
 decomposition in terms of the spectrum of $L$.

 There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. See \cite{HKBPS1,HKBPS2} for supercritical multi-type Galton-Waston processes, \cite{KBA1,KBA2,KBA3} for supercritical multi-type continuous time branching processes and \cite{ASHH} for general supercritical branching Markov processes 
% under some certain conditions. 
 under certain conditions. 
 In \cite{ARMP}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{MP2012} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition. 
% In this two paper, Milo\'s with his coauthor pictured connection 
These two papers made connections
 between CLT and what they call branching rate regimes. In \cite{RSZ}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
% Moverover, Compare with the results in \cite{ARMP,MP2012}, 
 Moverover, compared with the results in \cite{ARMP,MP2012}, 
 the limit distributions in \cite{RSZ} are non-degenerate. 
% In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, They also establish 
 In \cite{RSZ1,RSZ2,RSZ3,RSZ4}, Ren, Song and Zhang also established
 a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.

 All the results described above hold for systems with branching mechanisms with finite variance. %It's a natural  to ask that how to establish 
It is natural to ask whether there are 
counterparts of the central limit theorems for branching Markov processes and superprocesses %with infinite variance.  
with branching mechanisms of infinite variance.
 In \cite{MM}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems in small and critical branching rate cases,  
%but leave the central limit result unsolved for large rate case. 
but \cite{MM} contained no central limit result in the branching rate case.
In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MM}. For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit 
%theorem, which has no corresponds in \cite{MM}.
theorem, which has no counterpart in \cite{MM}.

>>>>

%%----Versions-----------------------------
% supCLT0128.tex 2018/01/28 by Renming
% supCLT0127.tex 2018/01/27 by Yanxia
% supCLT0124.tex 2018/01/24 by Jianjie
% supCLT0114.tex 2018/01/14 by Yanxia
% supCLT0107.tex 2018/01/07 by Jianjie
% supclt1231.tex 2018/12/14 by Zhenyao
% supclt1213.tex 2018/12/14 by Yanxia
% supclt1213.tex 2018/12/13 by Renming
% supclt1209.tex 2018/12/07 by Zhenyao
% supclt1207.tex 2018/12/07 by Renming
% supCLT1204.tex 2018/12/04 by Zhenyao
% supCLT1130.tex 2018/11/30 by Jianjie
% supCLT1124.tex 2018/11/24 by Zhenyao
% supCLT1115.tex 2018/11/15 by Jianjie
% supCLT9.tex ......... by Zhenyao
% supCLT8.tex ......... by Jianjie
% supCLT7.tex ......... by Zhenyao
% supCLT6.tex ......... by Jianjie
% supCLT5.tex ......... by Zhenyao
% supCLT4.tex ......... by Jianjie
% supCLT3.tex 2018/8/25 by Zhenyao
% supCLT2.tex 2018/8/13 by Jianjie
% supCLT1.tex 2018/7/24 by Zhenyao
% supCLT.tex 2018/6/29 by Jianjie
%---The preamble----------------------
\documentclass[12pt,a4paper]{amsart}
	\setlength{\textwidth}{\paperwidth}
	\addtolength{\textwidth}{-2in}
	\calclayout
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathtools}
	\mathtoolsset{showonlyrefs}
\usepackage{stackrel}
\usepackage{mathrsfs}
%\usepackage[backref=section]{hyperref}
\usepackage{hyperref}
\usepackage{comment}
%\usepackage[nobysame]{amsrefs}
\usepackage{amsthm}
	\theoremstyle{plain}
	\newtheorem{thm}{Theorem}[section]
	\newtheorem{lem}[thm]{Lemma}
	\newtheorem{prop}[thm]{Proposition}
	\newtheorem{cor}[thm]{Corollary}
	\newtheorem{conj}[thm]{Conjecture}
	\theoremstyle{definition}
	\newtheorem{defi}[thm]{Definition}
	\newtheorem{rem}[thm]{Remark}
	\newtheorem{exa}[thm]{Example}
	\newtheorem{asp}{Assumption}
	\numberwithin{equation}{section}
	\allowdisplaybreaks
%---Top matter------------------------------
\begin{document}
\title
    [CLT for Super-OU processes]
    {Stable Central Limit Theorems for Super OU Processes with Stable Branching}
\author
    [Y.-X. Ren, R. Song, Z. Sun and J. Zhao]
    {Yan-Xia Ren, Renming Song, Zhenyao Sun and Jianjie Zhao}
\address
    {Yan-Xia Ren
    \\ LMAM School of Mathematical Sciences \& Center for Statistical Science
    \\ Peking University
    \\ Beijing, P. R. China, 100871}
\email{yxren@math.pku.edu.cn}
\thanks{The research of Yan-Xia Ren is supported in part by NSFC (Grant Nos. 11671017  and 11731009).}
\address
    %{Renming Sond\\
    {Renming Song
    \\ Department of Mathematics
    \\ University of Illinois of Illinois at Urbana-Champaign
    \\ Urbana, IL 61801, USA}
\email{rsong@illinois.edu}
\thanks{The Research of Renming Song is support in part by a grant from the Simons Foundation (\#429343, Renming Song)}
\address
    {Zhenyao Sun
    \\ School of Mathematical Sciences
    \\ Peking University
    \\ Beijing, P. R. China, 100871}
\email{zhenyao.sun@pku.edu.cn}
\address
    {Jianjie Zhao
    \\ School of Mathematical Sciences
    \\ Peking University
    \\ Beijing, P. R. China, 100871}
\email{zhaojianjie@pku.edu.cn}
\begin{abstract}
    Consider a super Ornstein-Uhlenbeck processes (super-OU process) $(X_t)_{t\geq 0}$ with branching mechanism $\psi(z)=-\alpha z +\eta z^{1+\beta} + \psi_1(z),$ where $\alpha >0$ and $\beta\in (0,1)$ and $psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that $|\psi_1(z)| \leq C(|z|^2+|z|^{1+\gamma + \delta}).$
    For each testing function $f$ of polynomial growth, denote by $\kappa_f$ the order of $f$ in the spectral decomposition of $f$ in terms of the spectrum of the the mean semigroup of $X$.
    Conditioned on no-extinction, we establish some spatial central limit theorems for $\langle f, X_t \rangle$ in three different regimes:
    In the small branching rate case $\alpha\beta< \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/\|X_t\|^{\frac{1}{1+\beta}}$ converges weakly to a $(1+\beta)$-stable random variable.
    In the critical branching rate case  $\alpha\beta= \kappa_f b(1+\beta)$, $\langle f,X_t\rangle/(t\|X_t\|)^{\frac{1}{1+\beta}}$ converges weakly another $(1+\beta)$-stable random variable.
    In the large branching rate case  $\alpha\beta> \kappa_f b(1+\beta)$, we first prove that $e^{-(\alpha-\kappa(f)b)t}\langle f,X_t\rangle$ converges almost surely and in $L^{1+\gamma}$, for any $\gamma \in (0,\beta)$, and then established a central limit theorem, which says that, after proper centering and scaling, $\langle f,X_t\rangle$ again converges weakly to a $(1+\beta)$-stable random variable.
\end{abstract}
%\subjclass[2010]{60J80, 60F05}
%\keywords{}
%\date{}
\maketitle
%---Contents-----------------------
\section{Introduction}
%Moved and modified from below
\subsection{Motivation}
\label{sec: Motivation}
In this paper, we will establish some spatial central limit theorems for the super-OU process above. Precisely, we want to find $F_t$ and $G_t$ such that
    \frac{\langle f, X_t \rangle -G_t}{F_t}
    converges weakly to some non-degenerate random variable as $t\rightarrow\infty$, for some test functions $f$. 
    It turns out that the normalization $F_t$ depends on what we call branching rate regimes determined by the sign of $\alpha\beta-\kappa_f b (1+\beta)$, where $\kappa_f$ is the order of $f$ in the spectral decomposition in terms of the spectrum of $L$.

    There are many papers studying central limit theorems for branching processes, branching diffusions and superprocesses. 
    See \cite{KestenStigum1966A-limit,KestenStigum1966Additional} for supercritical multi-type Galton-Waston processes, \cite{Athreya1969Limit,Athreya1969LimitB,Athreya1971Some} for supercritical multi-type continuous time branching processes and \cite{AsmussenHering1983Branching} for general supercritical branching Markov processes under certain conditions. 
    In \cite{AdamczakMilos2015CLT}, Adamcazk and Milo\'s proved some central limit theorems for supercritical branching Ornstein-Uhlenbeck processes with binary branching mechanism and in \cite{Milos2012Spatial} Milo\'s proved some central limit theorems for supercritical super-OU processes with branching mechanisms satisfying a fourth moment condition. 
    These two papers made connections between CLT and what they call branching rate regimes. 
    In \cite{RenSongZhang2014Central}, Ren, Song and Zhang proved some central limit thoerems for supercritical super-OU processes with branching mechanisms satisfying only a second moment. 
    Moverover, compared with the results in \cite{AdamczakMilos2015CLT,Milos2012Spatial}, the limit distributions in \cite{RenSongZhang2014Central} are non-degenerate. 
    In \cite{RenSongZhang2014CentralB,RenSongZhang2015Central,RenSongZhang2017Central,RenSongZhang2017Functional}, Ren, Song and Zhang also established a series of central limit theorems for a large class of general supercritical branching Markov processes and super processes with spatially dependent branching mechanisms.
    All the results described above hold for systems with branching mechanisms with finite variance. 
    It is natural to ask whether there are counterparts of the central limit theorems for branching Markov processes and superprocesses with branching mechanisms of infinite variance.
    In \cite{MarksMilos2018CLT}, Marks and Milo\'s considered the limit behavior of supercritical branching Ornstein-Uhlenbeck processes with a special stable branching law. They established some central limit theorems in small and critical branching rate cases, but \cite{MarksMilos2018CLT} contained no central limit result in the branching rate case.
    In this paper, we consider a class of super-OU processes with more general stable branching mechanisms. 
    For small and critical branching rate cases, we obtain central limit theorems which are similar to the corresponding results for branching Ornstein-Uhlenbeck processes in \cite{MarksMilos2018CLT}. 
    For large branching rate case, we first establish  an almost sure convergence result, and then establish a central limit theorem, which has no counterpart in \cite{MarksMilos2018CLT}.

%Added
    {\bf ZS: I think this subsection should be extended with more literatures like: 
    \cite{AdamczakMilos2014U-statistics}, 
    \cite{EckhoffKyprianouWinkel2015Spines},
    \cite{EnglanderHarrisKyprianou2010Strong},
    \cite{IksanovKabluchko2016A-central}, 
    \cite{LiuRenSong2013Strong}, 
    \cite{Wang2018Central},
    \cite{IksanovKoleskoMeiners2018Stable-like},
    \cite{IksanovKoleskoMeiners2018Fluctuations},
    \cite{GrubelKabluchko2016A-functional},
    \cite{Heyde1970A-rate}, 
    \cite{Heyde1971Some}, 
    \cite{HeydeBrown1871An-invariance}, 
    \cite{HeydeLeslie1971Improved}, 
    \cite{BansayeDelmasMarsalleTran2011Limit}, 
    \cite{EnglanderWinter2006Law}, 
    \cite{Englander2009Law}, 
    \cite{Janson2004Functional}, 
    \cite{ChenRenWang2008An-almost}, 
    \cite{Wang2010An-almost}, 
    \cite{HartungKlimovsky2018The-phase}, 
    \cite{BansayeDelmasMarsalleTran2011Limit}, 
    \cite{Le2019Long}.
}
%end and modified from below
%\subsection{Model}\label{sec: main results}
\subsection{Main results}
\label{sec: main results}{}
	Let $d \in \mathbb N:= \{1,2,\dots\}$.
%moved and modifeid from below 
    Let $\mathbb R_+:= [0,\infty)$.
    Denote by $\mathcal B(\mathbb R^d, \mathbb R)$ the space of all $\mathbb R$-valued Borel measurable functions on $\mathbb R^d$.
    Denote by $\mathcal B(\mathbb R^d, \mathbb R_+)$ the space of all $\mathbb R_+$-valued Borel measurable functions on $\mathbb R^d$.
    Denote by $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
    For each $f,g\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ and $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
    For each $\mu \in \mathcal M(\mathbb R^d)$, write $\|\mu\| = \langle 1, \mu\rangle$.
%deletd
    %Write $\|\mu\|=\langle 1,\mu\rangle$ for each $\mu \in \mathcal M(\mathbb R^d)$. 
%end deleted
    We say a real-valued measurable function $f:(t,x)\mapsto f(t,x)$ on $\mathbb R_+\times \mathbb R^d$ is \emph{locally bounded} if for each $t\in \mathbb R_+$, we have 
    \sup_{s\in [0,t],x\in \mathbb R^d} |f(s,x)|<\infty.
%end moved from below
    Let $\xi=\{(\xi_t)_{t\geq 0}; (\Pi_x)_{x\in \mathbb R^d}\}$ be an $\mathbb R^d$-valued Ornstein-Uhlenbeck process (OU process) with generator
\begin{equation}
    Lf(x)
    = \frac{1}{2}\sigma^2\Delta f(x)-b x \cdot \nabla f(x),
    \quad  x\in \mathbb R^d, f \in C^2(\mathbb R^d),
\end{equation}
    where $\sigma$ and $b$ are positive constants.
%deleted
    %Denote by $(P_t)_{t\geq 0}$ the transition semigroup of $\xi$.
%end deleted
    %Let $\psi$ be the function on $\mathbb R_+$ defined by
    Let the \emph{branching mechanism} $\psi$ be a function on $\mathbb R_+$ which takes the form of
\begin{equation} \label{eq: honogeneou branching mechanism}
    \psi(z)=
    - \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    \quad  z \in \mathbb R_+,
\end{equation}
	where $\alpha > 0 $, $\rho \geq0$ and $\pi$ is a measure on $(0,\infty)$ with $\int_{(0,\infty)}y\wedge y^2 \pi(dy)< \infty$.
%new added
	It is known that $\alpha, \rho$ and $\pi$ are uniquelly determined by function $\psi$. 
	We refer to $\pi$ the \emph{L\'evy measure} of the branching mechanism $\psi$.
%end new added
%moved above
    %We use $\mathcal B(\mathbb R^d, \mathbb R)$ to denote   the space of all real-valued Borel measurable functions on $\mathbb R^d$ and use $\mathcal M(\mathbb R^d)$ the space of all finite Borel measures on $\mathbb R^d$.
	%For $f\in \mathcal B(\mathbb R^d, \mathbb R)$ and $\mu \in \mathcal M(\mathbb R^d)$, we write $\langle f,\mu\rangle = \int f(x)\mu(dx)$ whenever the integral makes sense.
    %We aslo use the notation $\|\mu\|=\langle 1,\mu\rangle$. 
    %For $f, g\in \mathcal B(\mathbb R^d, \mathbb R)$, we also write $\langle f, g\rangle = \int f(x)g(x) dx$ whenever the integral makes sense.
%end moved above
    %We say an $\mathcal M(\mathbb R^d)$-valued Markov process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a super Ornstein-Uhlenbeck process (super-OU process) with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
    We say an $\mathcal M(\mathbb R^d)$-valued Hunt process $X = \{(X_t)_{t\geq 0}; (\mathbb{P}_{\mu})_{\mu \in \mathcal M(\mathbb R^d)}\}$ is a \emph{super Ornstein-Uhlenbeck process (super-OU process)} with branching mechanism $\psi$, if for each non-negative bounded Borel function $f$ on $\mathbb R^d$, we have
\begin{equation} 
%\label{super}
    \mathbb{P}_{\mu}[e^{-\langle f,X_t \rangle}]
    = e^{-\langle V_tf, \mu \rangle},
    \quad t\geq 0, \mu \in \mathcal M(\mathbb R^d),
\end{equation}
	where $(t,x) \mapsto V_tf(x)$ is the unique locally bounded positive solution to the equation
\begin{equation} 
%\label{eq1}
	%V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(\xi_s,V_{t-s}f(\xi_s)\big)~ds\Big]
    V_tf(x) + \Pi_x \Big[ \int_0^t\psi\big(V_{t-s}f(\xi_s)\big)~ds\Big]
	= \Pi_x [f(\xi_t)],
    \quad x\in \mathbb R^d, t\geq 0.
\end{equation}	
    %The existence of superprocesses is well known, see \cite{Dynkin1993Superprocesses} for instance.
    The existence of such super-OU process $X$ is well known, see \cite{Dynkin1993Superprocesses} for instance.
%Added

	Denote by $\Gamma$ the gamma function. 
	In this paper, we will always assume that the following Assumption holds.
%End added

%Deleted
    %According to Subsection A.1, the branching mechanism $\psi$ can be extended to
    %$\mathbb C_+:=\{x+iy: x\in [0, \infty), y\in \mathbb R\}$ by
 %\[
    %\psi(z)=
    %- \alpha z + \rho z^2 + \int_{(0,\infty)} (e^{-zy} - 1 + zy) \pi(dy),
    %\quad  z \in \mathbb C_+,
%\]
    %which is continuous on $\mathbb C_+$ and is holomorphic on $\mathbb C_+^0:=
    %\{x+iy: x\in (0, \infty), y\in \mathbb R\}$ with derivative
%\begin{equation}
%\label{eq: deriavetive of the Poission part}
    %\psi'(z) := -\alpha + 2\rho z+ \int_{(0,\infty)} (1-e^{-zy}) y\pi(dy),
    %\quad z\in \mathbb C^0_+.
%\end{equation}

%\begin{asp}
%\label{asp: branching mechanism}
    %The branching mechanism takes the form of
%\[
    %\psi(z) = -\alpha z + \eta z^{1+\beta} + \psi_1(z),\quad z\in \mathbb C_+,
%\]
    %where $\alpha>0$, $\eta > 0$, $\beta \in (0,1)$ and $\psi_1$ is a function satisfying the condition that there exist $C >0$ and $\delta >0$ such that
%\[
    %|\psi_1(z)| \leq C(|z|^2+|z|^{1+\beta + \delta}),\quad z\in \mathbb C_+.
%\]
%\end{asp}
%end Deleted
%added
\begin{asp}
\label{asp: branching mechanism}
    There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that
\begin{equation}
\label{eq: asp of branching mechanism}
    \int_{(1,\infty)}y^{1+\beta +\delta}~\Big|\pi(dy)-\frac{\eta~dy}{\Gamma(-1-\beta)y^{2+\beta}}\Big| <\infty,
\end{equation}
	for some $\delta > 0$.
\end{asp}

	It will be showed in Subsection \ref{sec: branching mechanism} that if Assumption \ref{asp: branching mechanism} holds, then $\eta$ and $\beta$ are uniquelly determined by the L\'evy measure $\pi$.
	In the reminder of the paper, we will always write $\eta,\beta$ for the constants corresponding to $\pi$.
\begin{rem}
\label{rem: small enough delta}
	Note that $\delta$ is not uniquelly determined by $\pi$. 
	In fact, if $\delta>0$ is a constant such that \eqref{eq: asp of branching mechanism} holds, then replacing $\delta$ by any smaller positive number, \eqref{eq: asp of branching mechanism} still holds.
	Therefore, Assumption \ref{asp: branching mechanism} is equivalent to the following statements: There exist constants $\eta > 0$ and $\beta \in (0,1)$ such that, for each small enough $\delta>0$, \eqref{eq: asp of branching mechanism} holds.
\end{rem}

    Assumption \ref{asp: branching mechanism} says that there exists a constatn $\eta>0$ and $\beta > 0$ such that the Levy measure $\pi(dy)$ is not too far away from the measure $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$. 
    In particular, if $\pi(dy)$ equals to $\eta \Gamma(-1-\beta)^{-1}y^{-2-\beta} dy$, then the branching mechanism $\psi(z)$ takes the form of a stable branching
	$-\alpha z + \rho z^2 + \eta z^{1+\beta}$.
	It will be proved in Lemma \ref{lem: LlogL criterion} that under Assumption \ref{asp: branching mechanism}, the branching mechanism $\psi$ satisfies the $L \log L$ criteria, i.e. 
\[
	\int_{(1,\infty)} y\log y~\pi(dy) < \infty.
\]
